Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/concl.tex
include github URL
replace ambiguity with inconsistency
i think inconsistency more precisely captures what we mean

This paper presented the design and implementation of \textit{Nail},
a tool for parsing and generating complex data formats based on a
precise grammar.  Nail helps programmers avoid
memory corruption and ambiguity vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
maintaining a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.
Nail and all of the applications and grammars developed in this paper
are released as open-source software.

>>>>

This paper presented the design and implementation of \textit{Nail},
a tool for parsing and generating complex data formats based on a
precise grammar.  Nail helps programmers avoid
memory corruption and inconsistency vulnerabilities while reducing effort
in parsing and generating real-world protocols and file formats.
Nail achieves this by reducing the expressive power of the grammar,
maintaining a \emph{semantic bijection} between data formats and internal
representations.  Nail captures complex data formats by introducing
\emph{dependent fields}, \emph{streams}, and \emph{transforms}.
Using these techniques, Nail is able to support DNS packet and ZIP file
formats, and enables applications to handle these data formats in many
fewer lines of code.
Nail and all of the applications and grammars developed in this paper
are released as open-source software.

### 2014-09-10 paper/osdi14/design.tex
replace ambiguity with inconsistency
i think inconsistency more precisely captures what we mean

\item Eliminating redundancy in internal representations, such as
      storing both an explicit length field and an implicit length
      of a container data structure, to provide programmers
      an unambiguous view of the data, to avoid bugs such as in the Python ZIP library.

>>>>

\item Eliminating redundancy in internal representations, such as
      storing both an explicit length field and an implicit length
      of a container data structure, to provide programmers
      a consistent, unambiguous view of the data,
      to avoid bugs such as in the Python ZIP library.

### 2014-09-10 paper/osdi14/eval.tex
make spell
replace ambiguity with inconsistency
i think inconsistency more precisely captures what we mean

Nail also protects against parsing ambiguity vulnerabilities like the four others we studied. First,
Nail grammars explicitly encode duplicated information such as the redundant length fields in ZIP
that caused a vulnerability in the Python ZIP library. Second, the other three vulnerabilities exist
because multiple implementations of the same protocol disagree on some inputs. Hand-written protocol
parsers are not very reusable, as they build application specific data structures and are tightly
coupled to the rest of the code. Nail grammars, however, can be re-used between applications,
avoiding protocol misunderstandings.

@@

To evaluate whether Nail-based parsers are compatible with good
performance, we compare the performance of our DNS server to that of ISC
BIND 9 release 9.9.5~\cite{bind9}, a mature and widely used DNS server.
We simulate a load resembling that of an authoritative name server.
First, we generate domain names consisting of one or two labels randomly
selected from an English dictionary, and one label that is one of
three popular top-level domains (\cc{com}, \cc{net}, and \cc{org}).
Second, we randomly selected 90\% of these domains and created a zone
file that mapped these domain names to \cc{127.0.0.1}.  Finally, we used
the \cc{queryperf} tool provided with BIND to query each domain between
zero and three times, using a DNS server running on the local machine.
We used a single core of an Intel i7-3610QM system with 12GB of RAM.
The benchmark tool kept at most 20 queries outstanding at once, and
was configured to repeat the same randomized sequence of queries for
one minute.  We repeated each test seven times with 50,000 domain names,
restarting each daemon in between; we also repeated the tests with 1
million domain names, and found similar results.  We also performed one
initial dry run to warm the file system cache for the zone file.

>>>>

Nail also protects against parsing inconsistency vulnerabilities like the four others we studied. First,
Nail grammars explicitly encode duplicated information such as the redundant length fields in ZIP
that caused a vulnerability in the Python ZIP library. Second, the other three vulnerabilities exist
because multiple implementations of the same protocol disagree on some inputs. Hand-written protocol
parsers are not very reusable, as they build application specific data structures and are tightly
coupled to the rest of the code. Nail grammars, however, can be re-used between applications,
avoiding protocol misunderstandings.

@@

To evaluate whether Nail-based parsers are compatible with good
performance, we compare the performance of our DNS server to that of ISC
BIND 9 release 9.9.5~\cite{bind9}, a mature and widely used DNS server.
We simulate a load resembling that of an authoritative name server.
First, we generate domain names consisting of one or two labels randomly
selected from an English dictionary, and one label that is one of
three popular top-level domains (\cc{com}, \cc{net}, and \cc{org}).
Second, we randomly selected 90\% of these domains and created a zone
file that mapped these domain names to \cc{127.0.0.1}.  Finally, we used
the \cc{queryperf} tool provided with BIND to query each domain between
zero and three times, using a DNS server running on the local machine.
We used a single core of an Intel i7-3610QM system with 12GB of RAM\@.
The benchmark tool kept at most 20 queries outstanding at once, and
was configured to repeat the same randomized sequence of queries for
one minute.  We repeated each test seven times with 50,000 domain names,
restarting each daemon in between; we also repeated the tests with 1
million domain names, and found similar results.  We also performed one
initial dry run to warm the file system cache for the zone file.

### 2014-09-10 paper/osdi14/fig-motivation.tex
replace ambiguity with inconsistency
i think inconsistency more precisely captures what we mean

\begin{figure*}
\centering
\begin{tabular}{lllr}
\toprule
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
\midrule
  Memory corruption & 2013-5660 & Buffer overflow & 11\\
  Parser ambiguities & 2013-1462 & Multiple virus scanners interpret ZIP files incorrectly.& 4\\
  Semantic misunderstanding & 2014-2319 & Weak cryptography used even if user selects AES & 1\\
  \multicolumn{3}{l}{\bf Total vulnerabilities related to .zip processing }& \bf 16  \\
\bottomrule

>>>>

\begin{figure*}
\centering
\begin{tabular}{lllr}
\toprule
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
\midrule
  Memory corruption & 2013-5660 & Buffer overflow & 11\\
  Parser inconsistencies & 2013-1462 & Multiple virus scanners interpret ZIP files incorrectly.& 4\\
  Semantic misunderstanding & 2014-2319 & Weak cryptography used even if user selects AES & 1\\
  \multicolumn{3}{l}{\bf Total vulnerabilities related to .zip processing }& \bf 16  \\
\bottomrule

### 2014-09-10 paper/osdi14/motivation.tex
replace ambiguity with inconsistency
i think inconsistency more precisely captures what we mean

The Evasi0n jailbreak for iOS 6~\cite{evaders6} relies on the XNU kernel and
user-mode code-signing verifier interpreting executable metadata differently, so the code signature
sees different bytes at a virtual address than kernel maps into the process. The next version of iOS
added an explicit check for this particular metadata inconsistency. However, because parsing and
processing of the input data is still mixed, the jailbreakers could set a flag that re-introduced
the ambiguity after the check, but before signatures are verified~\cite{geohot-evasion}, which
allowed iOS 7 to be jailbroken.

>>>>

The Evasi0n jailbreak for iOS 6~\cite{evaders6} relies on the XNU kernel and
user-mode code-signing verifier interpreting executable metadata differently, so the code signature
sees different bytes at a virtual address than kernel maps into the process. The next version of iOS
added an explicit check for this particular metadata inconsistency. However, because parsing and
processing of the input data is still mixed, the jailbreakers could set a flag that re-introduced
the inconsistency after the check, but before signatures are verified~\cite{geohot-evasion}, which
allowed iOS 7 to be jailbroken.
